---
title: "Airbnb"
author: "Huiwen Duan"
date: "3/6/2019"
output: html_document
---
### Read summary data
```{r}
reviews <- read.csv("/Users/pan/Desktop/Winter 2019/Stats 140SL/HW/final_project/reviews.csv")
neighbourhoods <- read.csv("/Users/pan/Desktop/Winter 2019/Stats 140SL/HW/final_project/neighbourhoods.csv")
listings <- read.csv("/Users/pan/Desktop/Winter 2019/Stats 140SL/HW/final_project/listings.csv")

listingsFull <- read.csv("/Users/pan/Desktop/Winter 2019/Stats 140SL/HW/final_project/listingsFull.csv")
reviewsFull <- read.csv("/Users/pan/Desktop/Winter 2019/Stats 140SL/HW/final_project/reviewsFull.csv")
calendarFull <- read.csv("/Users/pan/Desktop/Winter 2019/Stats 140SL/HW/final_project/calendarFull.csv")
```

### Exploratory analysis
```{r}
# What do these datasets look like?
dim(listings)
str(listings)
summary(listings)
dim(reviews)
str(reviews)
summary(reviews)
dim(neighbourhoods)
str(neighbourhoods)
summary(neighbourhoods)
```
#### superhost versus score rating 
```{r}
bined_2<-rating %>% group_by(host_is_superhost) %>%summarise(count=n(),mean_rating=mean(review_scores_rating,na.rm = TRUE))
bined_2<-bined_2[2:3,]

ggplot(data = bined_2,aes(x = host_is_superhost,y = mean_rating))+geom_point(size = 10)+geom_line()+ylim(90,100)
```
#### Price Overview
```{r}
library(ggplot2)
library(dplyr)

summary(listings$price)

palette_1_colors <- c("#0DA3A0")

# Less than $500 distribution
priceGraph1 <- ggplot(listings[listings$price<500,], aes(price)) + 
  geom_histogram(fill=palette_1_colors, bins=200) +
  xlab("Price($)") + ylab("Count") +
  scale_fill_manual(values=palette_1_colors) +
  labs(x="Price($)", y="Count", title="Distribution of Airbnb Prices in Los Angeles")
priceGraph1

# More than 500 distribution
priceGraph2 <- ggplot(listings[listings$price>500,], aes(price)) + 
  geom_histogram(fill=palette_1_colors, bins=200) +
  xlab("Price($)") + ylab("Count") +
  scale_fill_manual(values=palette_1_colors) +
  labs(x="Price($)", y="Count", title="Distribution of Airbnb Prices in Los Angeles")
priceGraph2
```

#### Room types and Price
```{r}
sum(is.na(listings$price)) # No NA's in price column
sum(is.na(listings$room_type)) # No NA's in room_type column
unique(listings$room_type) # 3 room types
numRT1 <- length(listings$room_type[listings$room_type==unique(listings$room_type)[1]]) # Entire home/apt listings number in LA
numRT2 <- length(listings$room_type[listings$room_type==unique(listings$room_type)[2]]) # Private room listings number in LA
numRT3 <- length(listings$room_type[listings$room_type==unique(listings$room_type)[3]]) # Shared room listings number in LA
numRTVec <- c(numRT1, numRT2, numRT3)
meanRT1 <- mean(listings[listings$room_type==unique(listings$room_type)[1], ]$price) # Entire home/apt average price in LA
meanRT2 <- mean(listings[listings$room_type==unique(listings$room_type)[2], ]$price) # Private room average price in LA
meanRT3 <- mean(listings[listings$room_type==unique(listings$room_type)[3], ]$price) # Shared room average price in LA
meanRTVec <- c(meanRT1, meanRT2, meanRT3)
RT.df <- data.frame(Room_Type=c("Entire home/apt", "Private room", "Shared room"), Number_of_Listings=numRTVec, Average_Price=meanRTVec)
RT.df
pie(numRTVec, labels=c("Entire home/apt = 62.40%", "Private room = 33.35%", "Shared room = 4.25%"), main="Room Type Distribution in LA")
```
```{r}
listingsBigFive <- listings[listings$neighbourhood=="Culver City" | 
          listings$neighbourhood=="Santa Monica" | 
        listings$neighbourhood=="Downtown" |
          listings$neighbourhood=="Compton" |
          listings$neighbourhood=="Beverly Hills", ]
listingsBigFive <- listingsBigFive[,c(6,9,10)]

listingsBigFive

numa <- mean(listingsBigFive[listingsBigFive$neighbourhood=="Culver City" & listingsBigFive$room_type=="Entire home/apt",]$price)
numb <- mean(listingsBigFive[listingsBigFive$neighbourhood=="Culver City" & listingsBigFive$room_type=="Private room",]$price)
numc <- mean(listingsBigFive[listingsBigFive$neighbourhood=="Culver City" & listingsBigFive$room_type=="Shared room",]$price)

numd <- mean(listingsBigFive[listingsBigFive$neighbourhood=="Santa Monica" & listingsBigFive$room_type=="Entire home/apt",]$price)
nume <- mean(listingsBigFive[listingsBigFive$neighbourhood=="Santa Monica" & listingsBigFive$room_type=="Private room",]$price)
numf <- mean(listingsBigFive[listingsBigFive$neighbourhood=="Santa Monica" & listingsBigFive$room_type=="Shared room",]$price)

numg <- mean(listingsBigFive[listingsBigFive$neighbourhood=="Downtown" & listingsBigFive$room_type=="Entire home/apt",]$price)
numh <- mean(listingsBigFive[listingsBigFive$neighbourhood=="Downtown" & listingsBigFive$room_type=="Private room",]$price)
numi <- mean(listingsBigFive[listingsBigFive$neighbourhood=="Downtown" & listingsBigFive$room_type=="Shared room",]$price)

numj <- mean(listingsBigFive[listingsBigFive$neighbourhood=="Compton" & listingsBigFive$room_type=="Entire home/apt",]$price)
numk <- mean(listingsBigFive[listingsBigFive$neighbourhood=="Compton" & listingsBigFive$room_type=="Private room",]$price)
numl <- mean(listingsBigFive[listingsBigFive$neighbourhood=="Compton" & listingsBigFive$room_type=="Shared room",]$price)

numm <- mean(listingsBigFive[listingsBigFive$neighbourhood=="Beverly Hills" & listingsBigFive$room_type=="Entire home/apt",]$price)
numn <- mean(listingsBigFive[listingsBigFive$neighbourhood=="Beverly Hills" & listingsBigFive$room_type=="Private room",]$price)
numo <- mean(listingsBigFive[listingsBigFive$neighbourhood=="Beverly Hills" & listingsBigFive$room_type=="Shared room",]$price)

dfBigFivePrice <- data.frame(Neighborhood=c(rep("Culver City", 3), rep("Santa Monica", 3), rep("Downtown", 3), rep("Compton", 3), rep("Beverly Hills", 3)), Room_Type=rep(c("Entire home/apt", "Private room", "Shared room"), 5), Average_Price=c(numa,numb,numc,numd,nume,numf,numg,numh,numi,numj,numk,0,numm,numn,numo))
dfBigFivePrice

ggplot(dfBigFivePrice, aes(x=Neighborhood, y=Average_Price, fill = Room_Type)) +
  geom_bar(position = "dodge",stat="identity") + xlab("Neighborhood") + ylab("Price")+
  scale_fill_discrete(name = "Room Type") + 
  ggtitle("Room Type Prices in Five LA Neighborhoods?",
          subtitle = "Map showing Price of Listing Type by Neighborhood ") +
          theme(plot.title = element_text(face = "bold")) +
          theme(plot.subtitle = element_text(face = "bold", color = "grey35")) +
          theme(plot.caption = element_text(color = "grey68"))+scale_color_gradient(low="#d3cbcb", high="#852eaa")+
          scale_fill_manual("Property Type", values=c("#e06f69","#357b8a", "#7db5b8", "#59c6f3", "#f6c458")) +
          xlab("Neighborhood") + ylab("Price")

```

#### Neighborhoods and Price
```{r}
length(unique(listings$neighbourhood))
unique(listings$neighbourhood)
neighbourhoodPriceVec <- rep(NA, length(unique(listings$neighbourhood)))
for (i in 1:length(unique(listings$neighbourhood))) {
  neighbourhoodPriceVec[i] <- mean(listings[listings$neighbourhood==unique(listings$neighbourhood)[i], ]$price)
}
neighbourhoodPriceDF <- data.frame(Neighborhood=unique(listings$neighbourhood), Average_Price=neighbourhoodPriceVec)
neighbourhoodPriceDF
plot(neighbourhoodPriceDF)

neighbourhoodPriceDFOver500 <- neighbourhoodPriceDF[neighbourhoodPriceDF$Average_Price>500,]
neighbourhoodPriceDFOver500
plot(neighbourhoodPriceDF[neighbourhoodPriceDF$Average_Price>500,]$Neighborhood, neighbourhoodPriceDF[neighbourhoodPriceDF$Average_Price>500,]$Average_Price)
```



### Word Cloud
```{r}
splitnamecoloumn <- unlist(strsplit(as.character(listings$name), split=" "))
wordDF <- data.frame("word" = splitnamecoloumn)
wordDF <- wordDF %>% count(word, sort = TRUE) %>% 
  ungroup()

library("tm")
docs <- Corpus(VectorSource(splitnamecoloumn)) 
docs <- tm_map(docs, content_transformer(tolower))
docs = tm_map(docs,removePunctuation)
docs <- tm_map(docs, removeWords, c("in", "with", "&", "to", "the", "of", "and", "1", "2", " "))
newcorpusdf <- data.frame(text=sapply(docs, identity), 
    stringsAsFactors=F)
newcorpusdffiltered <- newcorpusdf %>% filter(text != "")
wordDF <- newcorpusdffiltered %>% count(text, sort = TRUE) %>% 
  ungroup()
library(RColorBrewer)
# install.packages("wordcloud")
library(wordcloud)
set.seed(789)
wordcloud(words = wordDF$text, 
          freq = wordDF$n,
          min.freq = 1000
          max.words=500, colors = c("#e06f69","#357b8a", "#7db5b8", "#59c6f3"))
```

```{r}
listings <- read.csv("listings.csv")
listingsFULL <- read.csv("listingsFULL.csv")
```
```{r}
head(listings)
head(listingsFULL)
listingsFULL <- listingsFULL[listingsFULL$market == "Los Angeles", ]
```

clean data first --> get LA  --> check
mean prices of LA airbnb
median prices or LA airbnb
total number of airbnbs in LA
number of airbnbs by neighbourhood
10 neighbourhood with highest number of airbnbs

number of airbnbs with different room_type
mean price of each room_type
median price of each room_type


number of airbnbs with different property_type
mean price of each property_type
median price of each property_type

mean prices of LA airbnb
```{r}
p <- substring(listingsFULL$price, 2) %>% as.numeric()
p2 <- na.omit(p)
mean(p2)
#$144.2907
```

median prices of LA airbnb
```{r}
median(p2)
#$100
```

total number of airbnbs in LA
```{r}
length(unique(listingsFULL$id))
#41938
```

number of airbnbs by neighbourhood
```{r}
lst0 <- listingsFULL %>% group_by(host_neighbourhood) %>% summarise_all(funs(n = n()))
lst0[order(-lst0$id_n), c(1,2)]
#The data frame contains county names and corresponding number of airbnbs in them.
```

10 neighbourhood with highest number of airbnbs
```{r}
lst2 <- lst0[order(-lst0$id_n), c(1,2)]
lst2[1:11, ]
#Top ten counties with the most airbnbs.
```

number of airbnbs with different room_type
```{r}
listingsFULL %>% group_by(room_type) %>% summarise_all(funs(n = n()))
#Entire home/apt --> 26276
#Private room --> 13834
#Shared room --> 1828
```

number of airbnbs with different property_type
```{r}
lst <- listingsFULL %>% group_by(property_type) %>% summarise_all(funs(n = n()))
lst[ , c(1,2)]
#The data frame contains property type and corresponding number of this type of airbnb.
```

The mean price for different room_type.
```{r}
lst4 <- listingsFULL
lst4$price <- substring(listingsFULL$price, 2) %>% as.numeric()
lst6 <- lst4[complete.cases(lst4$price), ]
lst5 <- lst6 %>% group_by(room_type) %>% summarise_at("price", mean, na.rm = F)
lst5
```

The top ten property_type that have the highest mean price.
```{r}
lst7 <- listingsFULL
lst7$price <- substring(listingsFULL$price, 2) %>% as.numeric()
lst8 <- lst7[complete.cases(lst7$price), ]
lst9 <- lst8 %>% group_by(property_type) %>% summarise_at("price", mean, na.rm = F)
lst9[order(-lst9$price),]
```
Relationship between number of accommodates, number of bedrooms and price.
```{r}
library(scatterplot3d)
lst10 <- listingsFULL
lst10$price <- substring(listingsFULL$price, 2) %>% as.numeric()
lst10$cleaning_fee <- substring(listingsFULL$cleaning_fee, 2) %>% as.numeric()

scatterplot3d(lst10$accommodates, lst10$bedrooms, lst10$price, type = "h", lwd = 0.5, xlab = "accommodates", ylab = "bedrooms", zlab = "price", xlim = 1:10, ylim = 1:10)

gn <- ggplot(lst10, aes(accommodates, price)) + geom_point() + geom_smooth()
gn
gnn <- ggplot(lst10, aes(bedrooms, price)) + geom_point() + geom_smooth()
gnn

#The number of accommodates may be one of the key factors people consider when they choose different types of rooms:
gn1 <- ggplot(lst10, aes(accommodates, price)) + geom_point() + geom_smooth()
gn1 + facet_wrap(~ room_type)
```

Relationship between length of description and review score rating for three types of rooms.
```{r}
library(gridExtra)
ls <- listingsFULL
for (i in 1:19556) {
  ls$deslength[i] <- str_length(ls$description[i])
}
g2 <- ggplot(ls, aes(deslength, review_scores_rating)) + geom_point() + geom_smooth()
g2 + facet_wrap(~ room_type)
```
### Leaflet Graph
```{r}
require(maptools)
require(sp)
require(RColorBrewer)
listings <- read.csv("listings.csv")
names(listings)
```
```{r}
pn <- data.frame(aggregate(listings[, c(10,11)], list(listings$neighbourhood), mean))
#summarise(pn)
range(listings$longitude)
range(listings$latitude)


file <- "l.a. county neighborhood (v6).shp"
la <- readShapePoly(file)
plot(la)
```
```{r}
la2 <- merge(la, pn, by.x="name", by.y="Group.1")
p <- colorRampPalette(c("darkseagreen1", "mediumorchid4"))(8)
palette(p)
price <- la2$price
summary(price)
data_levels <- cut(price, c(0, 85, 115, 150, 170,200, 500, 1000,2500))

```
```{r}
a <-plot(la2, col=as.numeric(data_levels), main="Average Price by Neighbourhood", lwd=0.0001,
         xlim = c(-118.9,-117), ylim=c(33.7, 34.8))
legend("bottomright", fill =p,
       legend = c("$0-85", "$85-115", "$115-150", "$150-170", "$170-200", "$200-500", "$500-1000", "$1000-2500"))
```

```{r}
listings2 <- read.csv("listingsFull.csv")
#names(listings2)
listings2$price <- as.integer(listings2$price)
listings2$security_deposit <- as.integer(listings2$security_deposit)
```
```{r}
sf <- data.frame(aggregate((listings2[,64] ), 
                            list(listings2$neighbourhood), mean))
#sf
summary(sf)
la4 <- merge(la, sf, by.x="name", by.y="Group.1")

sp <- la4$x
summary(sp)
p3 <- colorRampPalette(c("seashell", "seagreen3"))(5)
palette(p3)
data_levels3 <- cut(price, c( 1, 30, 40, 50, 100, 200))
#data_colors2 <- c("lightblue", "lightsalmon2", "indianred4", "red")
```
```{r}
c <-plot(la3, col=as.numeric(data_levels), main="Average Security Deposit by Neighbourhood", lwd=0.0001,
         xlim = c(-118.9,-117), ylim=c(33.7, 34.8))
legend("bottomright", fill =p3,
       legend = c("$1-30", "$30-40", "$40-50", "$50-100", "100-200"))
```

```{r}
sq <- data.frame(aggregate((listings2[, c(56,57)]), 
                            list(listings2$neighbourhood), mean))
sq$bedPerRoom = sq$beds/sq$bedrooms
summary(sq)
la3 <- merge(la, sq, by.x="name", by.y="Group.1")

bpr <- la3$bedPerRoom
summary(bpr)
p2 <- colorRampPalette(c("mistyrose", "lightsalmon3"))(6)
palette(p2)
data_levels2 <- cut(price, c(0, 1, 1.2, 1.3, 1.5, 2, 3))
#data_colors2 <- c("lightblue", "lightsalmon2", "indianred4", "red")
```
```{r}
b <-plot(la2, col=as.numeric(data_levels), main="Average Bed per Bedroom by Neighbourhood", lwd=0.0001,
         xlim = c(-118.9,-117), ylim=c(33.7, 34.8))
legend("bottomright", fill =p2,
       legend = c("0-1", "1-1.2", "1.2-1.3", "1.3-1.5", "1.5-2", "2-3"))
```

### Location analysis 
```{r}

ibrary(dplyr)
library(ggplot2)
listing<- read.csv("listings.csv",stringsAsFactors = FALSE)

names(listing)

#full<- read.csv("reviewsFull.csv",stringsAsFactors = FALSE)
plot(listing$minimum_nights~listing$price)
l<-lm(listing$price~listing$minimum_nights)
summary(l)
x<- data.frame(listing$price, breaks=cut(listing$price,breaks = 5, labels=c("100","200","300","400","500")) )

l2<-listing%>%filter(listing$neighbourhood %in% c("Beverly Hills","Compton","Santa Monica","Culver City","Downtown"))

mnights<- listing%>%filter(listing$neighbourhood %in% c("Beverly Hills","Compton","Santa Monica","Culver City","Downtown"))%>%group_by(neighbourhood, room_type)%>%summarise(mean = mean(minimum_nights))



listing%>%filter(listing$neighbourhood %in% c("Beverly Hills","Compton","Santa Monica","Culver City","Downtown"))%>%group_by(neighbourhood, room_type)%>%summarise(mean = mean(price))
mnights
ylim = (c(0,100))
boxplot(l2$minimum_nights~l2$room_type,ylim = (c(0,10)))

ggplot(mnights, aes(x=neighbourhood, y=mean, fill = room_type)) +
  geom_bar(position = "dodge",stat="identity") + xlab("Neighborhood") + ylab("Minimum Nights")+
  scale_fill_discrete(name = "Room Type")

ggplot(mnights, aes(x=neighbourhood, y=mean, fill = room_type)) +
  geom_bar(position = "dodge",stat="identity") + xlab("Neighborhood") + ylab("Minimum Nights")+
  scale_fill_discrete(name = "Room Type")



```{r}
listings2 <- read.csv("~/Desktop/airbnb/listings2.csv")
```

### Superhost Analysis
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
install.packages("lubridate")
library(lubridate)
```

```{r}
#create a new variable for the host time(last_scraped - host_since) and select only variables of interests
listings <- listings2 %>% mutate(last_scraped = ymd(last_scraped), host_since=ymd(host_since), host_time = round(as.numeric(difftime(last_scraped , host_since , units = c("days"))/365),1))%>% select(id, host_id, last_scraped, host_since,host_time, host_location, host_neighbourhood, host_has_profile_pic, host_identity_verified, host_is_superhost, host_response_rate,host_response_time, number_of_reviews, review_scores_communication,review_scores_rating,property_type,room_type,host_listings_count,review_scores_accuracy,instant_bookable,cancellation_policy)
listings$host_response_rate = as.integer(gsub("%","",listings$host_response_rate))
#combine distinct host ids
superhost <- filter(listings,host_is_superhost =='t')
notsuperhost <- filter(listings,host_is_superhost =='f')
sumsuper <- superhost %>% distinct(host_id, .keep_all = TRUE)
sumhost <- notsuperhost %>% distinct(host_id, .keep_all = TRUE)
```

```{r}
#some data exploratory between superhosts and non-superhosts
#number and percentage of superhosts
nrow(sumsuper)
nrow(sumsuper)/(nrow(sumsuper)+nrow(sumhost))
#average host_time 
mean(sumsuper$host_time)
mean(sumhost$host_time)
# average number of listings
mean(sumsuper$host_listings_count)
mean(sumhost$host_listings_count)
# average response rate
mean(sumsuper$host_response_rate,na.rm=TRUE)
mean(sumhost$host_response_rate,na.rm=TRUE)
# % identity_verified
sum(sumsuper$host_identity_verified=='t')/nrow(sumsuper)
sum(sumhost$host_identity_verified=='t')/nrow(sumhost)
# % instant_bookable
sum(sumsuper$instant_bookable=='t')/nrow(sumsuper)
sum(sumhost$instant_bookable=='t')/nrow(sumhost)
```

```{r}
sumsuper2 <- superhost %>% group_by(host_id) %>% summarise(reviews = sum(number_of_reviews)/n(), rating = sum(review_scores_rating)/n(), communication=sum(review_scores_communication)/n(), 
accuracy=sum(review_scores_accuracy)/n())sumhost2 <- notsuperhost %>% group_by(host_id) %>% summarise(reviews = sum(number_of_reviews)/n(), rating = sum(review_scores_rating)/n(), communication=sum(review_scores_communication)/n(), accuracy=sum(review_scores_accuracy)/n())
#average number of reviews
mean(sumsuper2$reviews)
mean(sumhost2$reviews)
#average rating scores
mean(sumsuper2$rating,na.rm=TRUE)
mean(sumhost2$rating,na.rm=TRUE)
#average communication scores
mean(sumsuper2$communication,na.rm=TRUE)
mean(sumhost2$communication,na.rm=TRUE)
#average accuracy scores
mean(sumsuper2$accuracy,na.rm=TRUE)
mean(sumhost2$accuracy,na.rm=TRUE)
```

```{r}
#response time distribution
responsetime <- listings %>% distinct(host_id, .keep_all = TRUE) %>% group_by(host_is_superhost) %>% summarise(within_an_hour=sum(host_response_time=='within an hour')/n(), within_a_few_hours=sum(host_response_time=='within a few hours')/n(), within_a_day=sum(host_response_time=='within a day')/n())
responsetime <- responsetime[-1,]
#some modifications for plot
rtplot <- gather(responsetime, "response_time", "percent", 2:4) %>% mutate(percent = round(percent*100, 1)) %>% mutate(percentWeight = ifelse(percent >= 50, percent * 4.5, ifelse(percent < 50 & percent >= 10, percent * 3.5, 
                                              ifelse(percent < 10 & percent >= 1, percent * 2.6, 1)))) %>% mutate(timeWeight = c(3,3,2,2,1,1)) %>% mutate(host_is_superhost = c("non-superhost","superhost","non-superhost","superhost","non-superhost","superhost"), percent=c("30.9%","66.5%","9.9%","12.1%","8.7%","4.0%"))
ggplot(rtplot, aes(x = host_is_superhost, y = response_time,label = percent)) + 
    geom_point(aes(size = percentWeight*2, colour = timeWeight)) + geom_text(hjust = 0.3, size = 3.5,colour="white") + scale_size(range = c(10, 45), guide = "none")  + scale_color_gradient(low = "rosybrown1", high = "indianred2")  +labs(title = "Response time of superhost and non-superhost") + theme(legend.title = element_blank(), plot.title = element_text(hjust = 0.5, size=13), axis.text.x = element_text(hjust=0.5, size=13), axis.text.y = element_text(hjust=0.5, size=13)) 
```

```{r}
#cancellation policy distribution
cp <- listings %>% distinct(host_id, .keep_all = TRUE) %>% group_by(host_is_superhost) %>% summarise(strict=sum(cancellation_policy == 'strict_14_with_grace_period')/n(), moderate=sum(cancellation_policy == 'moderate')/n(), flexible=sum(cancellation_policy == 'flexible')/n())
cp <- cp[-1,]
#some modifications for plot
cpplot <- gather(cp, "cancellation_policy", "percent", 2:4) %>% mutate(percent = round(percent*100, 1)) %>% mutate(percentWeight = ifelse(percent >= 40, percent * 4.5, ifelse(percent < 40 & percent >= 30, percent * 3.5, 
                                              ifelse(percent < 30 & percent >= 15, percent * 2.6, 1)))) %>% mutate(policyWeight = c(3,3,2,2,1,1)) %>% mutate(host_is_superhost = c("non-superhost","superhost","non-superhost","superhost","non-superhost","superhost"), percent=c("35.2%","37.1%","24.4%","44.3%","39.9%","18.4%"))
ggplot(cpplot, aes(x = host_is_superhost, y = cancellation_policy, label = percent)) + 
    geom_point(aes(size = percentWeight*2, colour = policyWeight)) + geom_text(hjust = 0.3, size = 3.5,colour="white") + scale_size(range = c(8, 40), guide = "none")  + scale_color_gradient(low = "rosybrown1", high = "indianred2")+labs(title = "Cancellation policy of superhost and non-superhost") + theme(legend.title = element_blank(), plot.title = element_text(hjust = 0.5, size=13), axis.text.x = element_text(hjust=0.5, size=13), axis.text.y = element_text(hjust=0.5, size=13))
```
```{r}
#room type distribution
roomtype <- listings %>% group_by(host_is_superhost) %>% 
  summarise(entire = sum(room_type=='Entire home/apt')/n(),private = sum(room_type=='Private room')/n(),shared = sum(room_type=='Shared room')/n())
roomtype <- roomtype[-1,]
#some modifications for plot
rplot <- gather(roomtype, "room_type", "percent", 2:4) %>% mutate(percent = round(percent*100, 1)) %>% mutate(percentWeight = ifelse(percent >= 60, percent * 4.5, ifelse(percent < 60 & percent >= 50, percent * 3.5, 
                                              ifelse(percent < 50 & percent >= 30, percent * 2.6, 1)))) %>% mutate(policyWeight = c(3,3,2,2,1,1)) %>% mutate(host_is_superhost = c("non-superhost","superhost","non-superhost","superhost","non-superhost","superhost"), percent=c("60.5%","67.1%","34.0%","31.6%","5.5%","1.2%"))
ggplot(rplot, aes(x = host_is_superhost, y = room_type, label = percent)) + 
    geom_point(aes(size = percentWeight*2, colour = policyWeight)) + geom_text(hjust = 0.3, size = 3.5,colour="white") + scale_size(range = c(8, 40), guide = "none")  + scale_color_gradient(low = "rosybrown1", high = "indianred2")+labs(title = "Room type of superhost and non-superhost properties") + theme(legend.title = element_blank(), plot.title = element_text(hjust = 0.5, size=13), axis.text.x = element_text(hjust=0.5, size=13), axis.text.y = element_text(hjust=0.5, size=13))
```


### Relative Occupancy Rate and leaflet plot)
### heat map of availability
```{r}
calendar <- calendar %>% mutate(booked = ifelse(available=="f", 1, 0))
groupedCalendar <- calendar %>% group_by(date = date) %>% summarise(totalBooked = sum(booked, na.rm = TRUE), totalListings = n()) %>% mutate(percent_booked = (totalBooked/totalListings)*100)
calendarHeat(groupedCalendar$date, groupedCalendar$percent_booked, ncolors = 100, color = "g2r", varname="Occupancy (Percentage) by Month")
```
### Leaflet
```{r}
LADF <- listings %>% select(neighbourhood,latitude,longitude) %>% group_by(neighbourhood) %>% summarise(latitude=round(mean(latitude),digits = 13),longitude=round(mean(longitude),digits = 13)) %>% as.data.frame()
maps<-listings %>% group_by(neighbourhood) %>% summarise(meanPrice=round(mean(price),digits = 2),num = n_distinct(neighbourhood)) %>% as.data.frame()
Maps <- inner_join(maps, LADF, by="neighbourhood")
LA <- leaflet() %>% addTiles() %>% 
  setView(lat = 34.0522, lng = -118.2437 , zoom = 10) %>%
  addMarkers(data = Maps, lng = ~longitude, lat = ~latitude, popup = as.character(Maps$meanPrice)) %>%
  addCircleMarkers(data = Maps, lng = ~longitude, lat = ~latitude, radius = 10, popup = as.character(Maps$num))
LA
```

### Initial Data Analysis 
```{r}
library(ggplot2)
listings<-read.csv("Desktop/140SL Final Project/listings.csv")
reviews<-read.csv("Desktop/140SL Final Project/reviews.csv")
d<-listings[!duplicated(listings$id),]
head(listings)
full_listings<-read.csv("Desktop/140SL Final Project/listings 2.csv")
variable.names(full_listings)
table(full_listings$review_scores_rating)
```

```{r}
table(reviews$date)
listings[listings$id == 6931,]
```
#### price vs score rating 
```{r}
library(dplyr)
rating<-full_listings[,c("id","host_is_superhost","experiences_offered","amenities","price","review_scores_rating")]
rating$price<-gsub("\\$", "", rating$price)
rating$price<-gsub("\\$", "", rating$price)
rating$price<-as.numeric(gsub("\\,", "", rating$price))


bined<-rating %>% group_by(review_scores_rating) %>% summarise(count=n(),mean_price=mean(price))
bined

ggplot(data = bined,aes(x = mean_price,y = review_scores_rating))+geom_point()+geom_smooth(method = lm,color= "red")
```
